### 2019-06-24 README.Rmd
Added Table 2 to README

---
output: github_document
---

@@

```{r pathEnrich}
# run pathEnrich using kegg_rno
## Genes of interest
sig_pe <- pathEnrich(gk_obj = kegg, gene_list = geneLists$sigGenes)
## Background
bkg_pe <- pathEnrich(gk_obj = kegg, gene_list = geneLists$background)
knitr::kable(head(sig_pe),
             caption = "Table 1. Head of sig_pe dataframe generated using pathEnrich", row.names = FALSE) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T)
```

@@

>>>>

---
output: github_document
always_allow_html: yes
---

@@

```{r pathEnrich, warning=FALSE}
# run pathEnrich using kegg_rno
## Genes of interest
sig_pe <- pathEnrich(gk_obj = kegg, gene_list = geneLists$sigGenes)
## Background
bkg_pe <- pathEnrich(gk_obj = kegg, gene_list = geneLists$background)
knitr::kable(head(sig_pe),
             caption = "Table 1. Head of sig_pe dataframe generated using pathEnrich", row.names = FALSE) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T)
```

@@

```{r pathEnrich_description, echo=FALSE}
# get column names
names <- colnames(sig_pe)
# Define column names
description <- c("KEGG ID",
                 "KEGG pathway description",
                 "PLACE HOLDER",
                 "PLACE HOLDER",
                 "Total number of pathways in KEGG release",
                 "PLACE HOLDER",
                 "PLACE HOLDER",
                 "Unadjusted p-value from Fisher's Exact test",
                 "False Discovery Rate (FDR)")
# Make dataframe
df1 <- data.frame(names, description)
colnames(df1) <- c("Column Names", "Column Description")

knitr::kable(df1,
             caption = "Table 2. Description of columns is dataframe generated by pathEnrich", row.names = FALSE) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
```
